Evaluating the Influence of Education on Current Unemployment Trends

### 2024-03-27 paper/paper.qmd
updated paper, llm usage and references

@@

>>>>

The dataset outlined in @tbl-data captures a comprehensive view of unemployment rates spanning from 2019 to 2023, segmented by different education levels. This rich dataset provides insights into the unemployment trends for three distinct age groups: youth, adults, and seniors, highlighting how economic fluctuations impact various demographics over time. The granularity of the data allows for an in-depth analysis of how education, as a key socio-economic factor, correlates with employment stability and job market resilience during periods of economic change.

@@

Our data set is comprised of data from the Labour Force Survey.
